### 2015-06-30 narrative/intro.tex

One of the key aspects of our approach is to allow the users to define the
utility (importance) of their data; in other-words, for each data object, users
need to come up with a way to define pieces of the object which have more
utility (more importance) . There are many clear research challenges faced with
this approach including: 1) How do we make this simple enough so that users can
do this, 2) can we come up with a model to allow the system to then make the
autonomic decisions to save the data which has the highest utility, and 3) can
we allow the back-end storage system to interact with this definition so that
it can optimize not just over one application but across all of the
applications.
 %
  In our simple scenario, a user wants to write 1 PB of data every hour
for checkpoint/restart, and they wish to write 500TB of data every 15
minutes to save analysis and visualization results which have already been reduced
using in situ reduction techniques. At this stage, they will ask the system to
write their data, and they would like to get an estimated time which they can
then figure out, through a series of rules, whether they want to write out all
of the data, postpone the write until a later time, or write a reduced amount
of data, along with some code
container to allow them to regenerate the data with a specified level of
accuracy.  Furthermore, they realize that the analysis data will be saved on
either the parallel file system, long-term tape storage, or on the campaign storage,
which is a medium-term storage
area with lower bandwidth than the parallel file system.
For each piece of data, the user will specify the lifetime so
that the data with the highest utility is kept around for the longest
period of time, but the data which has the least utility might be migrated to
lower layers of the storage hierarchy more quickly.

Since the data will be a collection of objects placed on the storage system,
some of the objects will be broken up into multiple pieces by ``plug-ins''
to the system which will allow data to be characterized in terms of the most
important pieces, and the next level of details. We can think of this as
something similar to an Adaptive Mesh Refinement scheme which keeps track of
the places where there are perhaps steep gradients (large errors on the
coarser views), and smaller errors. These then allows us to make decisions
about which sub-objects to save (all of the data, which will then go to
different layers) or just some of the sub-objects? The research questions
are numerous: How does the user specify their intentions? How does the user
prioritize the different sub-objects of the data? Where does the data go
into the storage hierarchy? Does the data get replicated in the lower tiers
of the hierarchy? When the user specifies the time they want the data saved,
how does this get into the storage system?

\subsection{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it needs to manage the data from
a given user request amongst all of the request and try to optimize the
entire system. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time. By requiring a certain quality
of service the system must potentially lock out users with lower currency
they want to place in the reading or writing of their data. The storage
system must also automatically move data from one tier of the storage to
another, without effecting the quality of service that it guarantees at the
time of questioning. The storage system must also look at ways to organize
data amongst all of the tiers of storage in one consistent way.

>>>>

One of the key aspects of our approach is to allow the users to define the
utility of their data; in other-words, the system should provide a
mechanism such that, for each data object, a user can specify pieces of the object
which have more utility (more importance).
Clearly there are many research challenges faced with
this approach including: 1) How do we make this simple enough so that users can
do this, 2) Can we define a model to allow the system to make
autonomic decisions to save the data which has the highest utility, and 3) Can
we allow the back-end storage system to interact with this model so that
it can optimize not just a single application but across all of the
applications.
 %
  In our simple scenario, a user wants to write 1 PB of data every hour
for checkpoint/restart, and they wish to write 500TB of data every 15
minutes to save analysis and visualization results which have already been reduced
using in situ reduction techniques. At this stage, they will ask the system to
write their data, and they would like to get an estimated time which they can
then figure out, through a series of rules, whether they want to write out all
of the data, postpone the write until a later time, or write a reduced amount
of data, along with some code
container to allow them to regenerate the data with a specified level of
accuracy.  Furthermore, they realize that the analysis data will be saved on
either the parallel file system, long-term tape storage, or on the campaign storage,
which is a medium-term storage
area with lower bandwidth than the parallel file system.
For each piece of data, the user will specify the lifetime so
that the data with the highest utility is kept around for the longest
period of time, but the data which has the least utility might be migrated to
lower layers of the storage hierarchy more quickly.

Since the data will be a collection of objects placed on the storage system,
some of the objects will be broken up into multiple pieces by ``plug-ins''
to the system which will allow data to be characterized first in terms of the most
important pieces, and then by subsequent levels of detail. We can think of this as
something similar to an Adaptive Mesh Refinement scheme which keeps track of
the places where there are features such as steep gradients, which contain large errors on the
coarser views, as opposed to other areas with smaller errors. These distinctions allow us to make decisions
about which sub-objects to save (all of the data, which will then go to
different layers) or just some of the sub-objects? The research questions
are numerous: How does the user specify their intentions? How does the user
prioritize the different sub-objects of the data? Where does the data go
into the storage hierarchy? Does the data get replicated in the lower tiers
of the hierarchy? When the user specifies the time they want the data saved,
how does this get into the storage system?

\subsection{Storage System Perspective}
\label{subsec:storage-perspective}
From the perspective of the storage system, it is necessary to manage the data from
a given user request amongst all of the requests from all users, and try to optimize the
entire system accordingly. Today the problem is that when a user writes there is a
tremendous amount of interference from other users on the system who may be
writing or reading at the same time. By requiring a certain quality
of service the system must potentially lock out users with lower currency
they want to place in the reading or writing of their data. The storage
system must also automatically move data from one tier of the storage to
another, without effecting the quality of service that it guarantees at the
time of questioning. The storage system must also look at ways to organize
data amongst all of the tiers of storage in one consistent way.
